\documentclass[12pt,notitlepage]{article}
\author{Leo Przybylski \\
\texttt{przybyls@arizona.edu}}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}

\title{Building a Path to Something That Works}


\begin{document}
\maketitle
\tableofcontents

\section{Desired Process}
\subsection{Actors}
\begin{description}
  \item[Environment Owner] the primary contact for a given environment
  \item[Environment Maintainer] the designated environment team personnel responsible for the refresh action.
  \item[Automation] non-human actor responsible for predefined processes.
  \item[Principals] not really responsible for anything. Just a group of individuals that are notified whenever
    a notification is required to be sent.
\end{description}

\subsection{The Script}

\begin{description}
\item[Environment Owner] creates a Jira task to refresh an environment with a specific build version and assigns
  \textbf{Principals}.
\item[Environment Maintainer] updates the Jira task when the process starts and notifies \textbf{Principals}.
\item[Environment Maintainer] updates the install log file that notes the desired build to install
\item[Automation] watching the install log notices a change and parses the file for information about the desired build.
\item[Automation] selects and installs the appropriate packages based on installation from the install log.
\item[Environment Maintainer] updates the original Jira task stating that the refresh is completed and notifies the \textbf{Principals}.
\end{description}


\section{Technical Details}
\subsection{The Install Log}
\begin{lstlisting}[caption=An example of the install log]
rsmart-1187    workflow,encrypt,demodata,conversion
kitt-1212-51    workflow,encrypt,demodata,conversion,rsmartdb,kittdb
\end{lstlisting}

The above describes that there were two builds done on that environment. The last record is
what the current build should be at. A cron process verifies that is the case by comparing the version
``kitt-1212-51'' to the current version in the system. The current version is stored in an
RPM database.

\lstset{basicstyle=\tiny,
  breaklines=true,
  includerangemarker=false}
\begin{lstlisting}
tomcat@uaz-kf-a02:/mosaic/data/KITT/RPMS/noarch> rpm -qi kfs-3.0-cfg.1212.51
Name        : kfs                          Relocations: (not relocatable)
Version     : 3.0                               Vendor: (none)
Release     : cfg.1212.51                   Build Date: Tue 20 Jul 2009 01:14:41 AM MST
Install Date: Wed 20 Jul 2009 10:44:58 AM MST      Build Host: uaz-kf-a00.mosaic.arizona.edu
Group       : System/Base                   Source RPM: kfs-3.0-cfg.1212.51.src.rpm
Size        : 279                              License: EPL
Signature   : (none)
Packager    : przybyls@arizona.edu
Summary     : Kuali Financial System Field Encryption
Description :
Mosaic KFS cfg Environment Web Application based on rSmart Vendor build 1212
with KITT modification set 51
\end{lstlisting}
\lstset{basicstyle=\small,
  breaklines=true,
  includerangemarker=false}

If the version doesn't exist, there will be no data at all. The cron process will then determine it needs
to install the necessary packages described and their dependencies. The install log is considered a log because
it has a record of every build. If there is ever a need to rollback to a previous build, the install log 
will simply look like:

\begin{lstlisting}[caption=Rollback scenario]
rsmart-1187    workflow,encrypt,demodata,conversion
kitt-1212-51    workflow,encrypt,demodata,conversion,rsmartdb,kittdb
rsmart-1187    workflow,encrypt,demodata,conversion
\end{lstlisting}

The above install log shows that ``kitt-1212-51'' was installed, but we can clearly see was 
rolled back because a previous line was copied to the end.

\subsection{Predefined Processes}

\begin{enumerate}
\item Environment Owner Creates Jira Task
\item Scripts run on environment to kick off update
\item tomcat restarts
\item Jira Task is updated and notifications are sent out
\end{enumerate}

Continuous Integration Weekly
\begin{itemize}
  \item Source Code Import
  \item Impex
\end{itemize}

Continuous Integration Daily
\begin{itemize}
  \item Sandbox Build
  \item selenium scripts (smoke tests against Sandbox Build)
  \item integration tests
\end{itemize}

Continuous Integration Bi-Daily
\begin{itemize}
  \item conversion scripts and CFG Copy
  \item unit tests  
\end{itemize}

\input{BuildProcessPlan.tex}

\end{document}
