\documentclass[12pt,notitlepage]{article}
\author{Leo Przybylski \\
\texttt{przybyls@arizona.edu}}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}

\title{CAS Extraction Integration}

\begin{document}
\maketitle

\lstset{basicstyle=\small,
  breaklines=true,
  includerangemarker=false}
\section{Technical Description}
CAS was extracted into a separate application. Unlike KEW, KSB, or KEN, CAS is a separate web 
application that runs independently. It can run within the same servlet container, or separately.

\subsection{edu.yale.its.tp.cas.client.filter.CASFilter}
\verb|KualiCasFilter| has been replaced by a newer \verb|CASFilter|. 
This filter still runs within the KFS application or any application that is built upon \emph{Kuali Rice.}
Like the \verb|KualiCasFilter|, the \verb|CASFilter| must also be declared within the KFS web.xml file; 
likewise, it also has a plethora of parameters that can be set in the declaration the determine its
overall behavior.

\subsection{context-cas.xml}
Because the \verb|kuali-cas-1.0.0.war| is distributed complete and packaged, the only way to manipulate
its settings (ie., datasource settings) is through a filtered \verb|context-cas.xml| located in the 
\verb|build/external/appserver/| path of KFS. It serves much the same purpose as the \verb|context.xml| 
file does for KFS.

\subsection{casclient-2.1.1.jar}
The \verb|SecureURL| and \verb|CASFilter| classes are included here. KFS uses these classes to handle validation
and url redirection between the \emph{kuali-cas} application and the \emph{kfs} application.

\section{Details}
\subsection{Modifications to build.properties}
\verb|build.properties| was modified so that a ``name'' is available. The ``name'' is pretty much the
same as \verb|${appserver.url}|. It just lacks the protocol. The reason for this is to configure \verb|CASFilter|
as described later.

\begin{lstlisting}
appserver.name=localhost:8080
appserver.url=http://${appserver.name}/
\end{lstlisting}

\subsection{Modifications to kfs-build.properties}
Any user building KFS with the new extracted CAS application must make the following adjustments
to the \verb|kfs-build.properties| file.

\begin{lstlisting}[caption=kfs-build.properties]
appserver.name=uaz-kf-a02.mosaic.arizona.edu:8240
appserver.url=http://${appserver.name}/
cas.application=${cas.application}
cas.war.file.path=${appserver.home}/webapps/
cas.datasource.username=${datasource.username}
cas.datasource.password=${datasource.password}
cas.datasource.url=${oracle.datasource.url}
cas.datasource.driver.class=oracle.jdbc.driver.OracleDriver
cas.require.https=false
cas.validate.password=false
\end{lstlisting}

\subsection{Modifications to configuration.properties}
The following was added to the \verb|build/project/configuration.properties| file so that
the \verb|KualiConfigurationService| will be able to get to the \verb|cas.require.https| property.
\begin{lstlisting}
cas.require.https=${cas.require.https}
\end{lstlisting}

\subsection{Modifications to web.xml}
A new \verb|CASFilter| is used instead of \verb|KualiCasFilter|. Parameters are pretty 
much the same as before, only there are now a couple more of note. First notice that 
\verb|${appserver.url}${cas.application}| is used. The reason is because CAS now runs as 
a separate application. This means, it no longer runs in \verb|${application.url}| like it
used to. We have to take a step back and use the \verb|${appserver.url}| instead.

\begin{description}
  \item[edu.yale.its.tp.cas.client.filter.serverName] Supposedly, this will fix our problems
    with proxies. This is set to expect \verb|serviceUrl| to come from \verb|serviceName|. 
    This is yet to be tested, but it is assumed that this will redirect relatively rather than
    strictly to the same url that was being accessed.
  \item[edu.yale.its.tp.cas.client.filter.wrapRequest] Sets the \verb|request.remoteUser| attribute.
    This is significant because the reference implementation \verb|AuthenticationService| shipped
    for KIM uses \verb|request.getRemoteUser()| to determine the principalName for the \verb|UserLoginFilter|.
    If this is not set, the principalName will be \verb|null| which will trigger a 
    \verb|NullPointerException|. Make sure this is set to \verb|true|.
\end{description}

\begin{lstlisting}
<web-app>
...
...
  <filter>
	<filter-name>cas</filter-name>
	<filter-class>edu.yale.its.tp.cas.client.filter.CASFilter</filter-class>
	<init-param>
	  <param-name>edu.yale.its.tp.cas.client.filter.loginUrl</param-name>
	  <param-value>${appserver.url}${cas.application}/login</param-value>
	</init-param>
	<init-param>
	  <param-name>edu.yale.its.tp.cas.client.filter.validateUrl</param-name>
	  <param-value>${appserver.url}${cas.application}/serviceValidate</param-value>
	</init-param>
	<init-param>
	  <param-name>edu.yale.its.tp.cas.client.filter.serverName</param-name>
	  <param-value>${appserver.name}</param-value>
	</init-param>
	<init-param>
	  <param-name>edu.yale.its.tp.cas.client.filter.wrapRequest</param-name>
	  <param-value>true</param-value>
	</init-param>
  </filter>
...
...
</web-app>
\end{lstlisting}

\subsection{Custom casclient-2.1.1.jar}
This is a temporary modification for build-1155 only. A \verb|rice-release-0-9-4-cas-br| was created
to address the extracted CAS application. As a result, a different \verb|CASFilter| and \verb|SecureURL|
are used in this branch. I had to checkout this branch and rebuild the casclient-2.1.1.jar to include
the \verb|rice-release-0-9-4-cas-br| specific \verb|CASFilter| and \verb|SecureURL| classes.

Also, KFS ships with its own \verb|edu.yale.its.tp.cas.util.SecureURL| class. I had to remove this
from our source code repository because it is redundant (there's already one in the \verb|casclient-2.1.1.jar|)
and it's not compliant with the \verb|rice-release-0-9-4-cas-br| branch.

I replaced the casclient-2.1.1.jar file in our source code repository. Hopefully, this will not be necessary
in subsequent builds of KFS.

\subsection{Overview of Build Process Changes}
Due to the new \verb|kuali-cas-1.0.0.war| and \verb|context-cas.xml| files and modifications
to the \verb|kfs-build.properties|, the build process has changed. A new \verb|kuali-cas.war| file is
copied to the \verb|${appserver.deploy.dir}| folder and the \verb|context-cas.xml| is copied to
\verb|${appserver.config.dir}| as \verb|kuali-cas.xml|.

All users building with the new extracted CAS will need to make the above described modifications
to the \verb|kfs-build.properties| file.

\subsection{Developer Integration}
KITT members should run the ``install-cas'' target of the \verb|vendor/kitt/deployment/ua-build.xml| file upon updating to build-1155. 
This is only necessary to do once ever. 

Running ``install-cas'' from Eclipse

\begin{enumerate}
  \item Make sure necessary changes were made to the \verb|kfs-build.properties|
  \item Add the \verb|ua-build.xml| to the ant view from \verb|vendor/kitt/deployment/|
  \item Run ``install-cas'' by double-clicking.
  \item \verb|SecureUrl| in \verb|work/src/edu/yale| is compatible with \verb|KualiCasFilter|
    and not \verb|CASFilter|. It should be removed from your class path (probably by deleting it)
    if you want to use the CASFilter.
  \item A custom \verb|casclient-2.1.1.jar| file is added to \verb|work/web-root/WEB-INF/lib|. Add it
    to your Eclipse build path.
    \begin{enumerate}
      \item click your right button on \verb|casclient-2.1.1.jar|
      \item Select ``Build Path''
      \item Select ``Add to Build Path''
      \item Your workspace will automatically start rebuilding
    \end{enumerate}
\end{enumerate}



\end{document}
