\documentclass[12pt,notitlepage]{article}
\author{Farooq Sadiq and Leo Przybylski}
\usepackage{graphicx}
\input{../../S5.tex}
\fulltitle{Continuous Integration}
\W \subtitle{Testing, Packaging, Deployment, EC2, Twitter, Jira, and SVN BFFs}

\W \affiliation{University of Arizona}

\newcommand{\Encapsulation}{\sf{\href{http://en.wikipedia.org/wiki/Information_hiding}{Encapsulation}}\rm{}}
\newcommand{\Abstraction}{\sf{\href{http://en.wikipedia.org/wiki/Abstraction}{Abstraction}}\rm{}}
\newcommand{\Inheritance}{\sf{\href{http://en.wikipedia.org/wiki/Inheritance_(computer_science)}{Inheritance}}\rm{}}
\newcommand{\ObjectModel}{\sf{\href{http://en.wikipedia.org/wiki/Object_model}{Object Model}}\rm{}}
\newcommand{\Modularity}{\sf{\href{http://en.wikipedia.org/wiki/Modularity_(programming)}{Modularity}}\rm{}}
\newcommand{\Polymorphism}{\sf{\href{http://en.wikipedia.org/wiki/Type_polymorphism}{Polymorphism}}\rm{}}
\newcommand{\MultiInheritance}{\sf{\href{http://en.wikipedia.org/wiki/Multiple_inheritance}{Multiple-Inheritance}}\rm{}}
\newcommand{\Kuali}{\emph{\href{http://www.kuali.org}{Kuali}}\rm{}}
\newcommand{\KualiFinancialSystem}{\emph{\href{http://www.kuali.org}{Kuali Financial System}}\rm{}}
\newcommand{\KFS}{\emph{\href{http://www.kuali.org}{KFS}}}
\newcommand{\MVC}{\emph{\href{http://en.wikipedia.org/wiki/Model-view-controller}{MVC}}}

\begin{document}
  \W \begin{s5presentation}
  \maketitle
  \W \begin{s5slide}
    \section{Overview}
    \subsubsection{The need}
    \begin{itemize}
      \item Guiding Points
      \item What Continuous Integration means to implementing schools
      \item Advantages of Continuous Integration
      \item Patterns of Continuous Integration with various development tools
      \item How the Kuali Foundation uses Continuous Integration
      \item The future of Continuous Integration at your institution
    and the Kuali Foundation.
    \end{itemize}
  \W \end {s5slide}
  \W \begin{s5slide}
    \section{Guiding Points}
      \subsubsection{Continuous Integration is not..}
      \begin{itemize}
      \end{itemize}
      \subsubsection{Continuous Integration is..}
      \begin{itemize}
        \item A scheduler
        \item Meant to manage environments
        \item A system administration dashboard
        \item Interactive
        \item A methodology
        \item Part of the development process
        \item Intended to improve software during all phases of the process cycle
      \end{itemize}
    \W \begin{s5notes}
    Before starting, there are some points about Continuous Integration that are relevant to 
    this presentation.

    Continuous Integration is not a tool or a scheduling system. You could probably accomplish
    similar with a scheduling system, but the advantages of Continuous Integration are not in scheduling. 
    It is a development methodology for iterative and incremental development processes; therefore,
    the advantages of Continuous Integration come out of your development process. When you shape
    your development process to include a system that ritualistically builds, tests, and packages your 
    software product, you immediately see the advantages. 
    \W \end{s5notes}    
  \W \end {s5slide}

  \W \begin{s5slide}
    \section{Advantages}
    \W \end{s5slide}

  \W \begin{s5slide}
    \section{Advantages}
    \begin{itemize}
      \item Isolated space for building
      \item Well-established CI system selection extensible to...
        \begin{itemize}
          \item Conform to your institution's development processes
          \item 
        \end{itemize}
      \item Validation through testing fully regressed
      \item Integrates with Change Management
    \end{itemize}
    \W \begin{s5notes}
      What makes CI any different from any other build process? Analyze a diagram that 
      shows the flow of developing a software feature. It isn't as simple as just periodically 
    building your software and testing it with automation. If one built a Continuous Integration tool for
    his/her software project from scratch starting with just periodically compiling and testing, the following
    might happen:
    \W \end{s5notes}
    \W \end{s5slide}
  
  \W \begin{s5slide}
    \W \section{What Needs to be Done Continuously?}
  \W \end {s5slide}
  \W \begin{s5slide}
    \W \section{What Needs to be Done Continuously?}
  \W \end {s5slide}
  \W \begin{s5slide}
    \W \section{Each is thrown out with each run}
  \W \end {s5slide}
  \W \begin{s5slide}
    \W \section{2 Parts}
  \W \end {s5slide}
  \W \end{s5presentation}
\end{document}
