\addcontentsline{toc}{part}{Exercise 4: Create Maintenance Document}
\part*{Exercise 4: \\
Setup Business Object}

\addcontentsline{toc}{section}{Exercise 5: Create Maintenance Document}
{\setlength{\baselineskip}%
  {0.0\baselineskip}
  \section*{\flushright Exercise r: \\
Setup Business Object}
  \hrulefill \par}

\addcontentsline{toc}{subsection}{Description}
\subsection*{Description}

\addcontentsline{toc}{subsection}{Goals}
\subsection*{Goals}

\addcontentsline{toc}{subsection}{Instructions}
\subsection*{Instructions}

\subsubsection*{1 Create Business Object Class}
Create a file in \textbf{work/src/org/kuali/kfs/sys/businessobject/}
called \textbf{FerpaCertification}
\begin{minted}{java}
/*
 * Copyright 2005-2008 The Kuali Foundation
 * 
 * Licensed under the Educational Community License, Version 2.0 (the "License");
 * you may not use this file except in compliance with the License.
 * You may obtain a copy of the License at
 * 
 * http://www.opensource.org/licenses/ecl2.php
 * 
 * Unless required by applicable law or agreed to in writing, software
 * distributed under the License is distributed on an "AS IS" BASIS,
 * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
 * See the License for the specific language governing permissions and
 * limitations under the License.
 */
package org.kuali.kfs.sys.businessobject;


/**
 * Ferpa Certification Business Object
 */
public class FerpaCertification extends PersistableBusinessObjectBase implements Inactivateable {
  
  private Long id;
  private String principalId;
  private String Person;

  /**
  * Default no-arg constructor.
  */
  
  public FerpaCertification() {
        super();
    }

    /**
     * Gets the id attribute.
     * 
     * @return Returns the id.
     */
    public String getId() {
        return id;
    }


    /**
     * Sets the id attribute value.
     * 
     * @param id The id to set.
     */
    public void setId(Long id) {
        this.id = id;
    }


    /**
     * Gets the principalId attribute.
     * 
     * @return Returns the principalId.
     */
    public Long getPrincipalId() {
        return principalId;
    }


    /**
     * Sets the principalId attribute value.
     * 
     * @param principalId The principalId to set.
     */
    public void setPrincipalId(String principalId) {
        this.principalId = principalId;
    }


    /**
     * Gets the person attribute.
     * 
     * @return Returns the person.
     */
    public String getPerson() {
        return person;
    }


    /**
     * Sets the person attribute value.
     * 
     * @param person The person to set.
     */
    public void setPerson(String person) {
        this.person = person;
    }
}
\end{minted}

\subsubsection*{2 Create Business DataDictionary Metadata}
\begin{minted}{xml}
\end{minted}

\subsubsection*{3 Create O/R Mapping}

\begin{minted}{xml}
\end{minted}

\subsubsection*{Add a link to the portal}

\newpage
{\setlength{\baselineskip}%
  {0.0\baselineskip}
  \section*{Notes}
  \hrulefill \par}