\documentclass[12pt,notitlepage]{article}
\author{Leo Przybylski}
\usepackage{graphicx}
\input{../KD2010.tex}
\fulltitle{LDAP Integration}
\W \subtitle{For Kuali Financials and Kuali Rice}

\W \affiliation{rSmart}

\newcommand{\Encapsulation}{\sf{\href{http://en.wikipedia.org/wiki/Information_hiding}{Encapsulation}}\rm{}}
\newcommand{\Abstraction}{\sf{\href{http://en.wikipedia.org/wiki/Abstraction}{Abstraction}}\rm{}}
\newcommand{\Inheritance}{\sf{\href{http://en.wikipedia.org/wiki/Inheritance_(computer_science)}{Inheritance}}\rm{}}
\newcommand{\ObjectModel}{\sf{\href{http://en.wikipedia.org/wiki/Object_model}{Object Model}}\rm{}}
\newcommand{\Modularity}{\sf{\href{http://en.wikipedia.org/wiki/Modularity_(programming)}{Modularity}}\rm{}}
\newcommand{\Polymorphism}{\sf{\href{http://en.wikipedia.org/wiki/Type_polymorphism}{Polymorphism}}\rm{}}
\newcommand{\MultiInheritance}{\sf{\href{http://en.wikipedia.org/wiki/Multiple_inheritance}{Multiple-Inheritance}}\rm{}}
\newcommand{\Kuali}{\emph{\href{http://www.kuali.org}{Kuali}}\rm{}}
\newcommand{\KualiFinancialSystem}{\emph{\href{http://www.kuali.org}{Kuali Financial System}}\rm{}}
\newcommand{\KFS}{\emph{\href{http://www.kuali.org}{KFS}}}
\newcommand{\MVC}{\emph{\href{http://en.wikipedia.org/wiki/Model-view-controller}{MVC}}}

\begin{document}
  \W \begin{s5presentation}
  \maketitle

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 1
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{Overview}

    \begin{itemize}
      \item What were the concerns?
      \item What were the risks?
      \item How did we do it?
      \item What is left?
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 2
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{Concerns}
    \begin{itemize}
    \item KFS version (3.0.1) vs. KC Version (2.0)
    \item Common action list
    \item Common/maintainable user base
    \item Common authorization maintenance
    \item Where is the data coming from?
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 3
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{More Concerns}
    \begin{itemize}
    \item Projects started unaware of each other
    \item Interaction with KFS
    \item KFS upgrade or separate rice installations?
    \item Dataset gaps?
    \item Schema gaps?
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 4
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{Projects Unaware}
    \begin{itemize}
    \item KFS implementation started before KC
    \item KC 1.0 features delayed until 2.0
    \item Many KC requisites were coupled to changes in more recent
      versions of Rice than KFS.
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 4
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{KFS Upgrade}
    \begin{itemize}
    \item UC Davis using custom version of KFS/Rice that allowed sharing of an
      action list provided the same version of Rice was used.
    \item KC 2.0 is compatible with Rice 1.0.2 and Rice 1.0.2.1.
    \item KFS 3.0.1 is incompatible with recent versions of Rice
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 5
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{More KFS Upgrade}
    \begin{itemize}
      \item KFS implementation at UA would require an upgrade
      \item Alternative to an upgrade is to use two action lists
      \item Concerns around this are data migration later
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 6
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{Risks}
    \begin{itemize}
      \item LDAP v. JDBC Datastore
      \item Who is responsible for integration?
      \item Timeline?
      \item Possibly huge integration hassle if proceeded with separate rice
        installations.
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 7
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{LDAP v. JDBC Datastore}
    \begin{itemize}
      \item JDBC is reference implementation and complete
      \item Some overriding and development is required
      \item Unsure whether all the data will come from a singular source
      \item KC Person has more information than is stored in KIM
      \item KFS and KC handle organizations differently with people
      \item How is the LDAP Server populated?
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 8
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{More LDAP v. JDBC Datastore}
    \begin{itemize}
      \item LDAP is live (queries server directly and immediately). Alternative
        is populating KIM tables with real users (approx. 30k including students).
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 9
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{Who is Responsible for the Integration?}
    \begin{itemize}
      \item Comes down to Java developers or SQL developers (resource management)
      \item LDAP (preferred) would require java developers
      \item JDBC Datastore would require populating the database with
        real data taken from an external system.
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 10
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{How did we do it?}
    \begin{itemize}
      \item Went with LDAP integration for users.
      \item Separate rice installations for now. Our answer is coming!
      \item Parallel deployment (running legacy and KC software together).
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 11
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{What separate rice installations}
    \begin{itemize}
      \item Went with LDAP integration for users.
      \item Separate rice installations for now. Our answer is coming!
      \item Parallel deployment (running legacy and KC software together).
    \end{itemize}
  \W \end{s5slide}

%%%%%%%%%%%%%%%%%%%$$$
%
% Slide 12
%
%%%%%%%%%%%%%%%%%%%%%%%
  \W \begin{s5slide}
    \section{What is left?}
    \begin{itemize}
      \item Common action lists/workflow
      \item Full KC software implementation
      \item Unit integration over web services
      \item Account creation over web services
    \end{itemize}
  \W \end{s5slide}
  
  \W \end{s5presentation}
\end{document}
