\documentclass[12pt,notitlepage]{article}
\author{Leo Przybylski \\
\texttt{przybyls@arizona.edu}}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}

\title{Remaining LDAP Integration Work}

\begin{document}
\maketitle

\lstset{basicstyle=\small,
  breaklines=true,
  includerangemarker=false}

\section{Overview}
Some other work than development is required to integrate LDAP into KFS environments.

\section{Integration Points}
\subsection{Conversion}
\subsubsection{Requirements}

Data required to be converted is
\begin{itemize}
  \item between UAID and principalId (all data that is using false principal ids needs to be replaced with real uaids).
  \item removal of constraints between entities and principals.
  \item removeal of entities.
\end{itemize}

\subsubsection{Work Done}
Keiko has put together some scripts to do map between UAID and principalId in conversion.

\subsubsection{Remaining Work}
\begin{itemize}
  \item Scripts need to be run in a sandboxed environment like STG for verification
  \item ids for principals not found in the \verb|ZZ_NETID| table need to be retrieved. 
\end{itemize}


\subsection{EDS}
The work required here is to be done by the Integration Team. 

\subsubsection{Requirements}

Requires EDS to
\begin{itemize}
\item support multiple affiliations
\item map campus code to affiliation
\item map separate employeeId to an affiliation
\item map separate department to an affiliation
\end{itemize}

\subsubsection{Work Done}
Leo added some default values within KFS to account for required fields. 

\subsubsection{Remaining Work}
Nothing on this has been done yet with the offical data in EDS. It still needs to be started. 
Leo contacted Duffy Gillman on the request process for this and is awaiting feedback.

\end{document}
